### 2025-01-26 our_article/MCM_article/article_file.tex
提交了论文和图片的重要更新

\documentclass{HZNUMCM}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{float}
\usepackage{svg}
\usepackage{mathrsfs}

\definecolor{customcolor}{HTML}{429938}

@@

%begin
\begin{document}
\showSummarySheet
\showContents

@@

        \begin{figure}[H]
          \centering
          \includegraphics[width=0.75\linewidth]{images/PlantMode.jpg}
          \caption{Agricultural Cycle in Southeast Asia}
          \label{fig:PlantMode}
        \end{figure}

@@

    \subsection{Model I: LVLG(Lokta-Volterra and Leslie-Gower) Model}
      We will first discuss the initial conditions of the model from the perspective of biological populations. 
      The vertical structure of tropical forests is typically divided into several layers, including the canopy layer, understory, shrub layer, and ground layer. 
      Each layer not only supports different plant species but also provides habitat and food sources for various animals. 
      Deforestation will severely disrupt the vertical structure of the tropical rainforest food web. 
      Therefore, our model assumes that at the initial time point following deforestation, 
      the vertical structure of the ecosystem above the ground retains only a portion of the ground layer. 
      All populations that previously depended on the canopy, understory, and shrub layers for habitat and food sources will have migrated out of the ecosystem.

@@

      \begin{figure}[H]
        \centering
          \begin{minipage}[b]{0.45\linewidth}
              \centering
              \includegraphics[height=5.5cm, keepaspectratio]{images/LGVGField.pdf} % 替换为你的第一张图片路径
              \caption{Schematic map for LGVG Model}
              \label{fig:LGVGField}
          \end{minipage}
        \hspace{0.05\linewidth}
          \begin{minipage}[b]{0.45\linewidth}
              \centering
              \includegraphics[height=5.5cm, keepaspectratio]{images/SimpleFoodWeb.pdf}
              \caption{Food web in LGVG Model}
              \label{fig:SimpleFoodWeb}
          \end{minipage}
        \end{figure}
      Set February-when rice has just been planted-as the start time.
      Around the start time, in the simplest case, when climate, soil, and other conditions are favorable, 
      only biological factors should be considered.
      If the population sizes of producers and primary consumers are used to describe the entire system, 
      the Lotka-Volterra Model\cite{wangersky1978lotka} and Leslie-Gower Model\cite{GUO20142850} can be applied as follows:
      \begin{equation}
        \begin{aligned}
          \frac{\mathrm{d}W_{crp}}{\mathrm{d}t}&=r_{crp}W_{crp}\left( 1-\frac{W_{crp}+\beta _{w\rightarrow c}W_{wd}}{\mathscr{K} _{crp}} \right) -\frac{A_{crp}W_{crp}W_{ins}}{1+B_{crp}W_{crp}}\\
          \frac{\mathrm{d}W_{wd}}{\mathrm{d}t}&=r_{wd}W_{wd}\left( 1-\frac{W_{wd}+\beta _{c\rightarrow w}W_{crp}}{\mathscr{K} _{wd}} \right) -\frac{A_{wd}W_{wd}W_{ins}}{1+B_{wd}W_{wd}}\\
          \frac{\mathrm{d}W_{ins}}{\mathrm{d}t}&=r_{ins}W_{ins}\left[ 1-\frac{D_{ins}W_{ins}}{1+E_{ins}\left( 0.6W_{crp}+0.4W_{wd} \right)} \right] -\frac{A_{ins}W_{ins}W_{bd}}{1+B_{ins}W_{ins}}\\
          \frac{\mathrm{d}W_{bd}}{\mathrm{d}t} &= r_{bd}W_{bd} \left[ 1 - \frac{D_{bd}W_{bd}}{1 + E_{bd}(0.2W_{ins} + 0.2W_{wd} + 0.6W_{crp})} \right]\\
        \end{aligned} 
      \end{equation}
      In general, these four equations introduce the natural growth term 
      \begin{equation}
        r_i W_i
      \end{equation}
      for population growth. 
      The first two equations incorporate the interspecific competition term 
      \begin{equation}
        \beta_{i \rightarrow j} W_i,
      \end{equation}
      the larger this term, the more intense the interspecific competition, and the slower the biomass growth rate of population $i$. 
      The first three equations consider the effect of predation through the term(e.g. the first one) 
      \begin{equation}
        \frac{A_{crp} W_{crp} W_{ins}}{1 + B_{crp} W_{crp}}. 
      \end{equation}
      The last two equations(e.g. the third one) include the term 
      \begin{equation}
        \frac{D_{ins} W_{ins}}{1 + E_{ins} \left( 0.6 W_{crp} + 0.4 W_{wd} \right)},
      \end{equation}
      which represents biomass reduction due to food scarcity. 
      In the denominator, one factor is weighted according to the predation ratio: the less food available, 
      the more predators there are, resulting in a slower growth rate of the predator population.

      \subsection{Model II: }
        Model I is quite simple and aims to construct a basic short-term model. 
        Considering the impact of long-term environmental factors, 
        in order to better simulate the long-term evolutionary behavior of the ecosystem model, 
        we will progressively introduce the effects of simplified agricultural cycles, 
        seasonality, soil fertility, and random factors on the system dynamics model. 
        Furthermore, we will consider the impact of chemical use, 
        specifically the application of herbicides and pesticides, on the system, 
        building upon this natural agricultural ecosystem model.

@@

          \begin{equation}
          \frac{\mathrm{d}W_{stw}}{\mathrm{d}t} = \frac{A_{stw} W_{stw} W_{ins}}{1 + B_{stw} W_{stw}} \quad (t \neq n)
          \end{equation}

          \begin{equation}
          W_{stw}|_{t=n} = W_{stw}|_{t=n-1} + 0.09 W_{crp}|_{t=n-1},\\
          n = 52k, 52k+17, 52k+34, \quad (k \geqslant 0, \, n \geqslant 1)
          \end{equation}

@@

        \subsubsection{Seasonality}
          The seasonal influences primarily include factors such as light, 
          climate (temperature, precipitation), and biological habits, 
          all of which have significant direct effects on both $r$ and $\mathscr{K}$ within populations. 
          Considering that many of these factors are difficult to quantify precisely, 
          we set sinusoidal perturbations in the periodic parameter $p(T)$ as follows:

@@

        \subsubsection{Soil Fertility}
        \subsubsection{Random Factor}
        \subsubsection{Chemical Use}
      \subsection{Model III: }
        \begin{figure}[H]
          \centering
          \includegraphics[width=0.5\linewidth]{images/food_web.pdf}
          \caption{Food web for NGLG Model}
          \label{fig:NGLG_FoodWeb}
        \end{figure}
      \subsection{Model IV: }
  \section{Application of the Models}

>>>>

\documentclass{HZNUMCM}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{float}
\usepackage{svg}
\usepackage{mathrsfs}
\usepackage{fvextra}
\definecolor{customcolor}{HTML}{429938}

@@

%begin
\begin{document}
\showSummarySheet
\newpage % 添加此行
\showContents

@@

        \begin{figure}[H]
          \centering
          \includegraphics[width=0.75\linewidth]{images/PlantMode.jpg}
          \caption{Agricultural Cycle in Southeast Asia\cite{IndoRice}}
          \label{fig:PlantMode}
        \end{figure}

@@

    \subsection{Model I: LVLG(Lotka-Volterra and Leslie-Gower) Model}
      We will first discuss the initial conditions of the model from the perspective of biological populations. 
      The vertical structure of tropical forests is typically divided into several layers, including the canopy layer, understory, shrub layer, and ground layer. 
      Each layer not only supports different plant species but also provides habitat and food sources for various animals.

      Deforestation will severely disrupt the vertical structure of the tropical rainforest food web. 
      Therefore, our model assumes that at the initial time point following deforestation, 
      the vertical structure of the ecosystem above the ground retains only a portion of the ground layer. 
      All populations that previously depended on the canopy, understory, and shrub layers for habitat and food sources will have migrated out of the ecosystem.

@@

      \begin{figure}[H]
        \centering
          \begin{minipage}[b]{0.45\linewidth}
              \centering
              \includegraphics[height=5cm, keepaspectratio]{images/LGVGField.pdf} % 替换为你的第一张图片路径
              \caption{Schematic map for LGVG Model}
              \label{fig:LGVGField}
          \end{minipage}
        \hspace{0.05\linewidth}
          \begin{minipage}[b]{0.45\linewidth}
              \centering
              \includegraphics[height=5cm, keepaspectratio]{images/SimpleFoodWeb.pdf}
              \caption{Food web in LGVG Model}
              \label{fig:SimpleFoodWeb}
          \end{minipage}
        \end{figure}
      Set February-when rice has just been planted-as the start time.
      Around the start time, in the simplest case, when climate, soil, and other conditions are favorable, 
      only biological factors should be considered.
      If the population sizes of producers and primary consumers are used to describe the entire system, 
      the Lotka-Volterra Model\cite{wangersky1978lotka} and Leslie-Gower Model\cite{GUO20142850} can be applied as follows:
      \begin{equation}
        \begin{aligned}
          \frac{\mathrm{d}W_{crp}}{\mathrm{d}t}&=r_{crp}W_{crp}\left( 1-\frac{W_{crp}+\beta _{w\rightarrow c}W_{wd}}{\mathscr{K} _{crp}} \right) -\frac{A_{crp}W_{crp}W_{ins}}{1+B_{crp}W_{crp}}\\
          \frac{\mathrm{d}W_{wd}}{\mathrm{d}t}&=r_{wd}W_{wd}\left( 1-\frac{W_{wd}+\beta _{c\rightarrow w}W_{crp}}{\mathscr{K} _{wd}} \right) -\frac{A_{wd}W_{wd}W_{ins}}{1+B_{wd}W_{wd}}\\
          \frac{\mathrm{d}W_{ins}}{\mathrm{d}t}&=r_{ins}W_{ins}\left[ 1-\frac{D_{ins}W_{ins}}{1+E_{ins}\left( 0.6W_{crp}+0.4W_{wd} \right)} \right] -\frac{A_{ins}W_{ins}W_{bd}}{1+B_{ins}W_{ins}}\\
          \frac{\mathrm{d}W_{bd}}{\mathrm{d}t} &= r_{bd}W_{bd} \left[ 1 - \frac{D_{bd}W_{bd}}{1 + E_{bd}(0.2W_{ins} + 0.2W_{wd} + 0.6W_{crp})} \right]\\
        \end{aligned} 
      \end{equation}
      In general, these four equations introduce the natural growth term 
      \begin{equation}
        r_i W_i
      \end{equation}
      for population growth. 
      The first two equations incorporate the interspecific competition term 
      \begin{equation}
        \beta_{i \rightarrow j} W_i,
      \end{equation}
      the larger this term, the more intense the interspecific competition, and the slower the biomass growth rate of population $i$. 
      The first three equations consider the effect of predation through the term(e.g. the first one) 
      \begin{equation}
        \frac{A_{crp} W_{crp} W_{ins}}{1 + B_{crp} W_{crp}}. 
      \end{equation}
      The last two equations(e.g. the third one) include the term 
      \begin{equation}
        \frac{D_{ins} W_{ins}}{1 + E_{ins} \left( 0.6 W_{crp} + 0.4 W_{wd} \right)},
      \end{equation}
      which represents biomass reduction due to food scarcity. 
      In the denominator, one factor is weighted according to the predation ratio: the less food available, 
      the more predators there are, resulting in a slower growth rate of the predator population.

    \subsection{Model II: CAGED(Conprehensive Agro-Ecosystem Dynamics) Model}
      Model I is quite simple and aims to construct a basic short-term model. 
      Considering the impact of long-term environmental factors, 
      in order to better simulate the long-term evolutionary behavior of the ecosystem model, 
      we will progressively introduce the effects of simplified agricultural cycles, 
      seasonality, soil fertility, and random factors on the system dynamics model. 
      Furthermore, we will consider the impact of chemical use, 
      specifically the application of herbicides and pesticides, on the system, 
      building upon this natural agricultural ecosystem model.

@@

        \begin{equation}
          \frac{\mathrm{d}W_{stw}}{\mathrm{d}t} = \frac{A_{stw} W_{stw} W_{ins}}{1 + B_{stw} W_{stw}} \quad (t \neq n)
        \end{equation}
        \begin{equation}
          W_{stw}|_{t=n} = W_{stw}|_{t=n-1} + 0.09 W_{crp}|_{t=n-1},\\
          n = 52k, 52k+17, 52k+34, \quad (k \geqslant 0, \, n \geqslant 1)
        \end{equation}

@@

      \subsubsection{Seasonality}
        The seasonal influences primarily include factors such as light, 
        climate (temperature, precipitation), and biological habits, 
        all of which have significant direct effects on both $r$ and $\mathscr{K}$ within populations. 
        Considering that many of these factors are difficult to quantify precisely, 
        we set sinusoidal perturbations in the periodic parameter $p(T)$ as follows\cite{GAKKHAR20061239}:

@@

      \subsubsection{Soil Fertility}
        The impact of soil fertility on plant growth is introduced. For simplicity in the model, 
        the effect of soil fertility on plant growth is divided into 
        the influence of the concentration of inorganic salts absorbed by the plants and the concentration of carbon dioxide.

        For the concentration of inorganic salts absorbed by the plants, 
        it is closely related to fertilizer concentration (affected by straw and chemical fertilizers), 
        decomposer activity, and the plant's growth stage. Taking rice as an example, during the seedling stage, 
        the concentration of inorganic salts in the plant is relatively low, with the rate of increase being positive; 
        from the tillering to jointing stage, the demand for inorganic salts rapidly increases, 
        and the concentration reaches a turning point; from the booting to flowering stage, 
        the rate of increase slows down until the concentration reaches its maximum; 
        in the milk to yellow ripening stage, the absorption of inorganic salts decreases, 
        and the concentration declines.
        %\cite{ref}.

        We use a Gaussian-like probability density function to fit the trend of inorganic salt concentration in the plant over each agricultural cycle, 
        expressed as:

        \begin{equation}
        C_{isc}(t) = \alpha_{isc} e^{-\frac{(t - T_{mc})^2}{\sigma_{isc}}}
        \end{equation}
        \begin{equation}
        C_{isw}(t) = \alpha_{isw} e^{-\frac{(t - T_{mw})^2}{\sigma_{isw}}}
        \end{equation}
        where $T_{mc}, T_{mw}$ represent the moment when the concentration of inorganic salts in the rice or weed reaches its maximum during a certain cycle; 
        $\alpha_{isc}, \alpha_{isw},  \sigma_{isc}, \sigma_{isw}$ correspond to the model parameters for rice or weeds, 
        which are determined by the fertilizer concentration (chemical fertilizers and straw), decomposer activity, and the plant's growth stage.
      \subsubsection{Random Factor}
      \subsubsection{Chemical Use}
        Considering that the application of herbicides during rice cultivation mainly occurs before sowing, 
        during the seedling stage, and the tillering stage, 
        we assume that herbicides are applied three times during an agricultural cycle, 
        with time points at week 0, week 3, and week 8. The herbicide application concentration is proportional to the current weed biomass. 
        Since the herbicide application frequency is low in this case, 
        we can neglect the specific negative effects of herbicides on rice (any minimal negative impact can be covered by the random process in Section 3.3.4).

        We consider weeds as the 'prey' of the herbicide. 
        Similar to the previous straw-insect model, 
        we can use a modified Lotka-Volterra predator-prey model, 
        where \( r_n \equiv 0 \).

        For the degradation of herbicide, we can use an exponential decay model. 
        This leads to the establishment of the weed-herbicide model:

        \begin{equation}
        C_{hc}|_{t=m} = C_{hc}|_{t=m-1} + \alpha W_{wd}|_{t=m}
        \end{equation}

        \begin{equation}
        \frac{W_{wd}}{dt} = r_{wd}W_{wd}\left(1 - \frac{W_{wd} + \beta_{c \rightarrow w} W_{crp}}{\mathscr{K}_{wd}}\right) - \frac{A_{wd}W_{wd}W_{ins}}{1 + \beta_{wd}W_{wd}} - \frac{A_{hc}W_{wd}C_{hc}}{1 + B_{hc}W_{wd}}
        \end{equation}

        \begin{equation}
        \frac{dC_{hc}}{dt} = -\alpha_{d}C_{hc}
        \end{equation}

    \subsection{Model III: }
      \begin{figure}[H]
        \centering
        \includegraphics[width=0.5\linewidth]{images/food_web.pdf}
        \caption{Food web for NGLG Model}
        \label{fig:NGLG_FoodWeb}
      \end{figure}
    \subsection{Model IV: }
  \section{Application of the Models}
